Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
added ideas of proofs

\sssec*{Idea of Proof:} To get $\supseteq$, we use the fact that

@@

@@

\[
	h^0 (X, k \halfcan ) = h^0(X, k \halfcan') + \lfloor k \frac{\alpha}{\beta}\rfloor.
\]

@@

@@

@@

@@

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to the
study of stacky canonical rings, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the Emory
University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
Zhang for helpful comments on this paper and thank Jorge Neves
for pointing out the bounds given by Miles Reid's work on the
maximal degrees of minimal generators and relations of spin
canonical rings in high genera. The first author would also like to
mention Joseph Harris and Evan O'Dorney for several enlightening
conversations related to Petri's Theorem. Finally, we gratefully
acknowledge the support of the National Science Foundation (grant
number DMS-1250467). We deeply appreciate all of the support that
has made our work possible.

>>>>

\sssec*{Idea of Proof:} To show $\supseteq$, we show $T \subset \initial(I),$ which follows immediately from $(1)$ and $(2)$. Then, $\subseteq$ follows from condition $(3)$, since $(1)$ implies $S$ is a basis, so no terms in $S$ can be contained in $\initial(I)$.

@@

\sssec*{Idea of proof:} The proof will be fairly involved. To show part (a), we first define an set of generators of $R_\halfcan$ over $R_{\halfcan'}$, with one generator corresponding to each best lower approximation. We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$, showing that the set of elements we produce forms a basis.

Next, part (b) immediately follows from an application of Lemma ~\ref{relations_from_generators_induction}, we only need verify the hypotheses of Lemma ~\ref{relations_from_generators_induction}. The first two hypotheses follow immediately from the construction of block order. Checking the third condition is quite technical, but the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***} give certain slope conditions, which are precisely what is needed to verify the third condition of Lemma ~\ref{relations_from_generators_induction}.

@@

\[
	h^0 (X, k \halfcan ) = h^0(X, k \halfcan') + \left\lfloor k \frac{\alpha}{\beta} \right\rfloor.
\]

@@

\sssec{Idea of proof:} The construction of the $y_{i,e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}. The inequality in Part (a) follows from the fact that $L$ is similar to $L'$, but with some of the $e_i$ incremented by $2$. Part (b) follows by noting that the generators in Part (a) form an independent set, as can be seen by noting that the sublattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J$. To check part (c) we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$. We note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to check this bound. Part (d) follows fairly easily from the definition of admissibility.

@@

\sssec*{Idea of Proof:} We check the theorem in two cases, depending on whether $\Delta > 0$. If $\Delta > 0$, we first check that the theorem holds for $L_X$ by adding in log points, and then check it holds for $L$ by raising the stabilizer orders of stacky points in a sequence of steps. When raising the stacky orders, it is important that we increment the stabilizer orders of the maximum possible number of stacky points at each step, so that the corresponding set will remain admissible. The check for $\Delta = 0$ is similar, although in this case we do not need to add in log points, only stacky points, and we will need to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.

@@

\sssec*{Idea of proof:} The method of this proof is almost identical to that of Theorem ~\ref{thm:g-1-main}. When $\delta > 0$, we first add in log points, and then increment the stabilizer orders of stacky points, checking that the theorem holds at each step. The more technical case occurs when $\delta = 0$, in which case we simply increment the stabilizer orders of stacky points starting from one of our base cases, and check that every stacky curve can be reached by a sequence of admissible incrementations from a base case.

@@

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to the
study of stacky canonical rings, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the Emory
University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
Zhang for helpful comments on this paper. We also thank Jorge Neves
for pointing out the bounds given by Miles Reid's work on the
maximal degrees of minimal generators and relations of spin
canonical rings in high genera. The first author would also like to
mention Joseph Harris and Evan O'Dorney for several enlightening
conversations related to Petri's Theorem. Finally, we gratefully
acknowledge the support of the National Science Foundation (grant
number DMS-1250467). We deeply appreciate all of the support that
has made our work possible.
